How do galaxies get assigned to halos? \\ Searching for assembly bias in the SDSS galaxy clustering

### 2016-09-28 text/ms.tex
changed a few words in discussion

Our constraints on the assembly bias parameters fall into two main categories. First, the satellite 
assembly bias parameter $\asat$ and the second, the central assembly bias parameter $\acen$. As shown in Figure \ref{fig:bias}, for all the eight luminosity threshold samples in the SDSS DR7 data, our constraints on the parameter $\asat$ are 
consistent with zero. On the other hand, our constraints on the parameter $\acen$---albeit not tightly constrained---show a trend which can be summarized as the following. In the most luminous galaxy samples, i.e. $M_{\rm r} < -21.5$ and $M_{\rm r} < -21$, $\acen$ is poorly constrained and the constraints are equivalent to zero. As we probe less luminous samples, $M_{\rm r} < -20.5 , -20, -19.5$, our constraints on $\acen$ shift towards positive values, with the $M_{\rm r}<-20$ sample favoring the highest values for $\acen$. Furthermore, the posterior constraints on the assembly bias parameters in the slightly fainter samples, i.e. $M_{\rm r} < -19$ and i.e. $M_{\rm r} < -18.5$, are consistent with zero. In the faintest galaxy sample, i.e. $M_{\rm r} < -18$, our constraints favor negative values of $\acen$.

The underlying theoretical consideration for explaining the assembly bias of the central 
and satellite galaxies are different. The large scale clustering---or the two halo term in the galaxy clustering---is mainly governed by the clustering of the central galaxies. The central galaxy clustering can be thought as the weighted average over the halo clustering. The large scale bias of the dark matter halo clustering depends not only on mass, but on other the properties of halos beyond mass, such as concentration (\citealt{weschler2006,gao2007,miyatake2016}), spin (\citealt{gao2007}), formation time (\citealt{gao2007, li2008}), and the maximum circular velocity over the accretion history of the halo $V_{\rm max}$ (\citealt{sunayama2016}).

In particular, findings of (\citealt{weschler2006,sunayama2016})
have demonstrated that for the halos with mass bellow the collapse mass ($M \leq M_{\rm col} \simeq 10^{12.5}\; M_{\odot} $) the large scale bias of high-$V_{\rm max}$ or high-$c$ halos at a fixed halo mass is larger than that of the low-$V_{\rm max}$ or low-$c$ halos. This signal reverses and weakens for the high mass halos ($M \geq M_{\rm col}$). Note that the halo concentration traces the maximum circular velocity $V_{\rm max}$ such that halos with higher $V_{max}$ have higher concentration and vice versa (see \citealt{prada2012}). For halos described by NFW profile, at a fixed halo mass, halos with higher values of concentration have higher values of $V_{\rm max}$.

Furthermore, investigation of the scale-dependence of halo assembly bias has shown that the ratio of the bias of high-$V_{\rm max}$ halos and the low-$V_{\rm max}$ halos has a bump-like feature in the quasi-linear scales $\sim$ 0.5 $\mathrm{Mpc}h^{-1}-5\mathrm{Mpc}h^{-1}$. From the theoretical standpoint, this phenomenon has been attributed to a population of distinct halos with $\log M \sim 11.7$ (in the units of $h^{-1}M_{\odot}$) the present time that are close to the most massive groups and clusters (\citealt{sunayama2016}, and see \citealt{more2016} for the observational investigation of this signal by means of galaxy-galaxy lensing). The clustering of these population of halos is therefore dictated by that of the massive halos which cluster more strongly. Also note that this signal vanishes for the high mass halos.

@@

Figure \ref{fig:wpmodel} demonstrates the 68$\%$ and 95$\%$ percent posterior predictions for the projected 2PCF $w_{p}$ from the occupation model without assembly bias (shown in red) and the occupation model with assembly bias (shown in blue) for all eight luminosity-threshold samples. For the brightest galaxies, $M_{r} < -21.5$ and $M_{r} < -21.0$, the posterior prediction of $w_{p}$ from the two models are consistent with one another. Note that these galaxies reside in the most massive halos ($M > M_{\rm col}$) for which the scale-dependence of the halo assembly bias and the difference between the large-scale bias of the high-$c$ and low-$c$ halos become negligible.

Figure \ref{fig:wpres} shows the fractional difference between the 68$\%$ and 95$\%$ percent posterior predictions of $w_p$ and the SDSS data. It is evident from Figure \ref{fig:wpres} that some improvement on modeling the clustering of the samples of $L_{\star}$ and slightly less brighter than $L_{\star}$ galaxies can be achieved by employing the model complex halo occupation model with assembly bias. As a result of apportioning more central galaxies to the high-$c$ halos with respect to the low-$c$ halos, in the samples with luminosity thresholds of $M_{\rm r}<-20.5, -20, -19.5, -19$, the posterior predictions for $w_{p}$ are slightly improved in the intermediate scales ($1\sim 2 \; \mathrm{Mpc} h^{-1}$) and larger scales. This can be also noted in significantly lower $\chi^{2}$ values---at the cost more model flexibility and higher degrees of freedom---achieved by the assembly bias model in these luminosity-threshold samples (see Table \ref{tab:constraints}).

@@

Finally, In the faintest sample ($M_{\rm r} < -18$), negative constraints on the parameter $\acen$ results in higher expected number of centrals in the low-$c$ halos, which at a fixed halo mass, cluster less strongly (in the low mass halos). This affects both the large scale bias and the intermediate regimes as a result of the scale-dependent bump feature (see Figures \ref{fig:wpmodel} and \ref{fig:wpres}). Furthermore, the model with assembly bias provides better fit to the SDSS data in this luminosity-threshold sample.

The luminosity dependent trend in the constraints on the central assembly bias for the six dimmest samples can be attributed to the fact that the halo concentration is highly correlated with the maximum circular velocity $V_{\rm max}$ which is a tracer of the potential well of dark matter halos (\citealt{prada2012}). In a dark matter halo described by an NFW profile, the depth of the gravitational potential well of dark matter halos can be directly measured by the maximum circular velocity $V_{\rm max}$ (\citealt{vmax_potential}). In particular, the magnitude of the potential well at the center of an NFW halo---where the central galaxy is assumed to reside---scales as $V_{\rm max}^{2}$:
\beq
\Phi(r=0) = -\Big(\frac{V_{\rm max}}{0.465}\Big)^{2},
\eeq
 where $\Phi(r=0)$ is the central potential of an NFW profile. Note that $V_{\rm max}$ is also the quantity often used in the abundance matching technique in which the luminosity of galaxies is monotonically matched to $V_{\rm max}$ (see for example \citealt{reddick2013, hod_vs_sham, halodemographic}). The trend between the constraint on $\acen$ and the luminosity threshold of the samples may suggest that at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies in the dimmest sample ($M_{\rm r}<$-18 , -18.5) tend to reside in dark matter halos with shallower gravitational well, and as we probe brighter galaxy samples ($M_{\rm max}<$-19 , -19.5, -20, -20.5), at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies have a tendency to reside in dark matter halos with deeper gravitational potential well.

The satellite assembly bias can only alter the galaxy clustering at small-to-intermediate scales. Assigning more satellite galaxies to lower (or higher) concentration halos affects the one-halo term through increasing the satellite-satellite pair counts $\langle N_{\rm sat} N_{\rm sat} \rangle$. This results in boosting the small-scale clustering, but as pointed out in \citealt{decorated}, the amount by which small-scale clustering increases also depends on the sign of the central assembly bias parameter $\acen$. Formation history of the halos can lead to the dependence of the abundance of subhalos on halo concentration (\citealt{zentner2005, mao2015}) at fixed halo mass, and since the occupation of the satellite galaxies is related to the abundance of subhalos, the satellite occupation might depend halo concentration.

However, our results suggest that for all the 8 luminosity-threshold samples, the satellite assembly bias parameter is largely unconstrained and consistent with zero. we do not expect the galaxy clustering data to be a sufficient statistics for obtaining constraints on the satellite assembly bias. Group statistics probes the high mass end of the galaxy--halo connection and is sensitive to the parameters governing the satellite population (see \citealt{sham_gmf, 2016arXiv160701782H}), and therefore these measurements may shed light on investigating assembly bias in the satellite population.

It is important to note that the halo mass range in which the central assembly bias $\acen$ affects the central galaxy population is the mass range that satisfies the condition $0<\langle N_{\rm cen}|M \rangle<1$. As a result, larger scatter parameter $\sigmam$ increases the dynamical mass range in which assembly bias affects the galaxy clustering. Note that in the regimes for which we obtain tighter constraints on $\acen$, the best-estimate value of the scatter parameter $\sigmam$ appears to be higher in the model with assembly bias. This is also evident in Figure \ref{fig:posterior}. The tendency of the model with assembly bias to push $\sigmam$ to higher values can be attributed to the tendency of this model to increase the effective dynamical mass range of $\acen$.

As evident in Table \ref{tab:constraints}, in the HOD model with assembly bias, the constraints found on the scatter parameter are not tight. This is in keeping with the results of \citealt{guo2015} (which uses the same SDSS data) according to which, the scatter parameter remains largely unconstrained when only $n_{g}$ and $w_{p}$ are used as observables. Note that scatter is better constrained for the most luminous galaxy samples (this is attributed to the steep dependence of the halo bias and halo mass function on halo mass in the high mass end). But since these samples live in the most massive halos, we do not expect the tighter constraints on scatter to help us constrain the central assembly bias parameter. \citealt{guo2015} shows that by employing additional measurements such as the monopole ($\xi_{0}$), quadruple ($\xi_{2}$), hexadecapole ($\xi_{4}$), one can obtain tighter constraints on the scatter parameter. Tightening of constraints on the scatter parameters leads to reduction of uncertainty in the inferred central assembly bias parameter.

As shown in Table \ref{tab:constraints}, our constraints on the underlying standard HOD model obtained from the model with assembly bias and the model without assembly bias are in good agreement. The only cases in which there are mild tensions between the constraints found from the two models on the underlying HOD parameters, are the $M_{\rm r}<-20$ and the $M_{\rm r}<-20.5$ samples. However, these tensions are within one-sigma uncertainties. For instance, Figure \ref{fig:posterior} shows that in the $M_{\rm r}<-20.5$ sample, the constraint on the parameter $\alpha$ found from the model without assembly bias favor slightly higher values than the constraint found from the model with assembly bias. Also the scatter parameter $\sigmam$ is more tightly constrained in the standard HOD model. However, it is important to emphasize that these constraints are still in agreement with each other within a one-sigma level. \citealt{arz2014} shows that in the catalogs that exhibit significant levels of assembly bias, using a simple mass-only occupation model can lead to considerable biases in inference of the galaxy--halo connection parameters. Although we cannot rule out moderate level of assembly bias in our findings, we do not find any considerable discrepancy between the two models in terms of estimating the underlying HOD parameters.

A few galaxy--halo connection methods have been proposed in the literature that give rise to assembly bias in the galaxy population. \citealt{arz2014} demonstrates that the abundance matching techniques based on $V_{\rm max }$ (as introduced in \citealt{hw2013,reddick2013}) exhibit some levels of assembly bias.

We aim to provide a comparison between the levels of assembly bias in these mock catalogs and the mock catalogs predicted from our constraints on the decorated HOD model for $L_{\star}$ type galaxies. In particular, we consider the abundance matching catalogs produced by \citealt{hw2013}. These catalogs have been extensively studies for potential systematic effects of galaxy assembly bias on cosmological (\citealt{edHOD-weinberg}) and HOD (\citealt{arz2014}) inferences. This abundance matching catalog was built based on the $\mathtt{Bolshoi}$ $N$-body simulation (\citealt{Klypin2011}) using the adaptive refinement tree code (ART \citealt{art}). The Box size for this simulation is 250 $h^{-1} \rm{Mpc}$, the number of simulation particles is 2048$^3$, the mass per simulation particle $m_{\rm p}$ is $1.35 \times 10^{8} \; h^{-1} M_{\odot}$, and the gravitational softening length $\epsilon$ is 1 $h^{-1} \rm{kpc}$. The halos and subhalos in this simulation are identified using the ROCKSTAR algorithm (\citealt{rockstar}). 
The \citealt{hw2013} catalogs make use of $V_{\rm peak}$ (maximum $V_{\rm max}$ throughout the assembly history of halo) as the subhalo property to be matched to galaxy luminosity.

As noted by both \citealt{arz2014},and \citealt{edHOD-weinberg}, these galaxy mock catalogs show significant levels of assembly bias. This has been shown by investigating the difference in $w_{p}$ between the randomized mock catalogs and the original mock catalogs. Randomization is performed in a procedure described in \citealt{arz2014}: the central galaxies among all halos within each of the halo mass bins (with width of 0.1 dex). In each mass bin, once the centrals have been shuffled, the satellite systems are shuffled among all halos in that mass bin, preserving their relative distance to the center of halo. This procedure preserves the HOD, but erases any dependence of the galaxy population on the assembly history of halos such that, assembly bias is erased in the randomized catalog.

For $L_{\star}$ galaxies, the difference in $w_{p}$ between the randomized and the \citealt{hw2013} catalogs is shown in Figure \ref{fig:randomized} with the red curves. As previously noted by \citealt{arz2014} these catalogs and as it can be seen in Figure $\ref{fig:randomized}$ the difference in $w_{p}$ is only significant in large scales. This means that in these catalogs, only the central galaxies are affected by assembly bias which is in agreement with our findings.

Furthermore, by making random draws from the posterior pdf over the parameters of the model, creating mock catalogs with these random draws, and computing the difference in $w_{p}$ between the randomized catalogs and the origin and catalogs (shown with blue curves in Figure \ref{fig:randomized}), we note that our findings follow the same trend. That is, we see no difference in the small scale clustering and significant differences as we move towards larger scales. Similar to \citealt{hw2013} catalogs, assembly bias becomes less significant as we probe brighter galaxy samples. Furthermore, we notice that our mock catalogs favor more modest levels of assembly bias as the fractional difference in $w_{p}$ is smaller in our mock catalogs.

>>>>

Our constraints on the assembly bias parameters fall into two main categories. First, the satellite 
assembly bias parameter $\asat$ and the second, the central assembly bias parameter $\acen$. As shown in Figure \ref{fig:bias}, for all the eight luminosity-threshold samples in the SDSS DR7 data, our constraints on the parameter $\asat$ are 
consistent with zero. On the other hand, our constraints on the parameter $\acen$---albeit not tightly constrained---show a trend which can be summarized as the following. In the most luminous galaxy samples, i.e. $M_{\rm r} < -21.5$ and $M_{\rm r} < -21$, $\acen$ is poorly constrained and the constraints are equivalent to zero. As we probe less luminous samples, $M_{\rm r} < -20.5 , -20, -19.5$, our constraints on $\acen$ shift toward positive values, with the $M_{\rm r}<-20$ sample favoring the highest values for $\acen$. Furthermore, the posterior constraints on the assembly bias parameters in the slightly fainter samples, i.e. $M_{\rm r} < -19$ and i.e. $M_{\rm r} < -18.5$, are consistent with zero. In the faintest galaxy sample, i.e. $M_{\rm r} < -18$, our constraints favor negative values of $\acen$.

The underlying theoretical consideration for explaining the assembly bias of the central 
and satellite galaxies are different. The large scale clustering---or the two halo term in the galaxy clustering---is mainly governed by the clustering of the central galaxies. The central galaxy clustering can be thought as the weighted average over the halo clustering. The large scale bias of the dark matter halo clustering depends not only on mass, but also on the other properties of halos beyond mass, such as concentration (\citealt{weschler2006,gao2007,miyatake2016}), spin (\citealt{gao2007}), formation time (\citealt{gao2007, li2008}), and maximum circular velocity of the halo $V_{\rm max}$ (\citealt{sunayama2016}).

In particular, findings of \citet{weschler2006} and \citet{sunayama2016}
have demonstrated that for halos with mass bellow the collapse mass ($M \leq M_{\rm col} \simeq 10^{12.5}\; M_{\odot} $) the large scale bias of high-$V_{\rm max}$ (or equivalently high-$c$ halos at a fixed halo mass) is larger than that of the low-$V_{\rm max}$ (low-$c$ halos). This signal reverses and weakens for the high mass halos ($M \geq M_{\rm col}$). Note that the halo concentration traces the maximum circular velocity $V_{\rm max}$ such that halos with higher $V_{max}$ have higher concentration and vice versa (see \citealt{prada2012}). For halos described by NFW profile, at a fixed halo mass, halos with higher values of concentration have higher values of $V_{\rm max}$.

Furthermore, investigation of the scale-dependence of halo assembly bias has shown that the ratio of the bias of high-$V_{\rm max}$ halos and the low-$V_{\rm max}$ halos has a bump-like feature in the quasi-linear scales $\sim$ 0.5 $\mathrm{Mpc}h^{-1}-5\mathrm{Mpc}h^{-1}$. From the theoretical standpoint, this phenomenon has been attributed to a population of distinct halos with $M \sim 10^11.7 \; h^{-1}M_{\odot}$ at the present time that are close to the most massive groups and clusters (\citealt{sunayama2016}, and see \citealt{more2016} for the observational investigation of this signal by means of galaxy-galaxy lensing). The clustering of these population of halos is therefore dictated by that of the massive halos. Note that this scale-dependent bias feature vanishes as we probe high mass halos.

@@

Figure \ref{fig:wpmodel} demonstrates the 68$\%$ and 95$\%$ posterior predictions for the projected 2PCF $w_{p}$ from the occupation model without assembly bias (shown in red) and the occupation model with assembly bias (shown in blue) for all eight luminosity-threshold samples. For the brightest galaxies, $M_{r} < -21.5$ and $M_{r} < -21.0$, the posterior prediction of $w_{p}$ from the two models are consistent with one another. Note that these galaxies reside in the most massive halos ($M > M_{\rm col}$) for which the scale-dependence of the halo assembly bias and the difference between the large-scale bias of the high-$c$ and low-$c$ halos become negligible.

Figure \ref{fig:wpres} shows the fractional difference between the 68$\%$ and 95$\%$ posterior predictions of $w_p$ and the SDSS data. It is evident from Figure \ref{fig:wpres} that some improvement on modeling the clustering of the samples of $L_{\star}$ and slightly less brighter than $L_{\star}$ galaxies can be achieved by employing the more complex halo occupation model with assembly bias. As a result of apportioning more central galaxies to the high-$c$ halos relative to the low-$c$ halos, in the samples with luminosity thresholds of $M_{\rm r}<-20.5, -20, -19.5, -19$, the posterior predictions for $w_{p}$ are slightly improved in the intermediate scales ($1\sim 2 \; \mathrm{Mpc} h^{-1}$) and large scales. This can be also noted in significantly lower $\chi^{2}$ values---at the cost more model flexibility and higher degrees of freedom---achieved by the assembly bias model in these luminosity-threshold samples (see Table \ref{tab:constraints}).

@@

Finally, In the faintest sample ($M_{\rm r} < -18$), negative constraints on the parameter $\acen$ results in higher expected number of centrals in the low-$c$ halos, which at a fixed halo mass, cluster less strongly. This affects both the large scale bias and the intermediate regimes as a result of the scale-dependent bump feature (see Figures \ref{fig:wpmodel} and \ref{fig:wpres}). Furthermore, the model with assembly bias provides better fit to the SDSS data in this luminosity-threshold sample.

The luminosity dependent trend in the constraints on the central assembly bias for the six dimmest samples can be attributed to the fact that the halo concentration is highly correlated with the maximum circular velocity $V_{\rm max}$ which is a tracer of the potential well of dark matter halos (\citealt{prada2012}). In a dark matter halo described by an NFW profile, the depth of the gravitational potential well of dark matter halos can be directly measured by the maximum circular velocity $V_{\rm max}$ (\citealt{vmax_potential}). In particular, the magnitude of the potential well at the center of an NFW halo---where the central galaxy is assumed to reside---scales as $V_{\rm max}^{2}$. More specifically, we have:
\beq
\Phi(r=0) = -\Big(\frac{V_{\rm max}}{0.465}\Big)^{2},
\eeq
 where $\Phi(r=0)$ is the central potential of an NFW profile. Note that $V_{\rm max}$ is also the quantity often used in the abundance matching technique in which the luminosity of galaxies is monotonically matched to $V_{\rm max}$ (see for example \citealt{reddick2013, hod_vs_sham, halodemographic}). The trend between the constraint on $\acen$ and the luminosity threshold of the samples may suggest that at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies in the dimmest samples ($M_{\rm r}<$-18 , -18.5) tend to reside in dark matter halos with shallower gravitational well. As we probe brighter galaxy samples ($M_{\rm max}<$-19 , -19.5, -20, -20.5), at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies have a tendency to reside in dark matter halos with deeper gravitational potential well.

The satellite assembly bias can only alter the galaxy clustering at small-to-intermediate scales. Assigning more satellite galaxies to lower (or higher) concentration halos affects the one-halo term through increasing the satellite-satellite pair counts $\langle N_{\rm sat} N_{\rm sat} \rangle$. This results in boosting the small-scale clustering, but as pointed out in \citealt{decorated}, the amount by which small-scale clustering increases also depends on the sign of the central assembly bias parameter $\acen$. Formation history of the halos can lead to the dependence of the abundance of subhalos on halo concentration (\citealt{zentner2005, mao2015}) at fixed halo mass, and since the occupation of the satellite galaxies is related to the abundance of subhalos, the satellite occupation might depend on halo concentration.

However, our results suggest that for all the 8 luminosity-threshold samples considered in this study, the satellite assembly bias parameter is largely unconstrained and consistent with zero. We do not expect the galaxy clustering data to be a sufficient statistics for obtaining constraints on the satellite assembly bias. Group statistics probes the high mass end of the galaxy--halo connection and is sensitive to the parameters governing the satellite population (see \citealt{sham_gmf, 2016arXiv160701782H}). Therefore these measurements may shed light on potential presence of assembly bias in the satellite population.

It is important to note that the halo mass range in which the central assembly bias $\acen$ affects the central galaxy population is the mass range that satisfies the condition $0<\langle N_{\rm cen}|M \rangle<1$. As a result, larger scatter parameter $\sigmam$ increases the dynamical mass range in which assembly bias affects the galaxy clustering. Note that in the regimes for which we obtain tighter constraints on $\acen$, the best-estimate value of the scatter parameter $\sigmam$ appears to be higher in the model with assembly bias. This is evident in Figure \ref{fig:posterior}. The tendency of the model with assembly bias to push $\sigmam$ to higher values can be attributed to the tendency of this model to increase the effective dynamical mass range of central assembly bias.

As evident in Table \ref{tab:constraints}, in the HOD model with assembly bias, the constraints found on the scatter parameter are not tight. This is in keeping with the results of \citet{guo2015} which uses the same SDSS data and finds that the scatter parameter remains largely unconstrained when only $n_{g}$ and $w_{p}$ are used as observables. Note that scatter is better constrained for the most luminous galaxy samples (this is attributed to the steep dependence of the halo bias and halo mass function on halo mass in the high mass end). But since these samples live in the most massive halos, we do not expect the tighter constraints on scatter to help us constrain the central assembly bias parameter. \citet{guo2015} shows that by employing additional measurements such as the monopole ($\xi_{0}$), quadruple ($\xi_{2}$), and hexadecapole ($\xi_{4}$), one can obtain tighter constraints on the scatter parameter. Tightening of constraints on the scatter parameters can lead to reduction of uncertainty in the inferred central assembly bias parameter.

As shown in Table \ref{tab:constraints}, our constraints on the underlying standard HOD model obtained from the model with assembly bias and the model without assembly bias are in good agreement. The only cases in which there are mild tensions between the constraints found from the two models on the underlying HOD parameters, are the $M_{\rm r}<-20$ and the $M_{\rm r}<-20.5$ samples. However, these tensions are within one-sigma uncertainties. For instance, Figure \ref{fig:posterior} shows that in the $M_{\rm r}<-20.5$ sample, the constraint on the parameter $\alpha$ found from the model without assembly bias favor slightly higher values than the constraint found from the model with assembly bias. Also the scatter parameter $\sigmam$ is more tightly constrained in the standard HOD model. However, it is important to emphasize that these constraints are still in agreement with each other within a one-sigma level. \citet{arz2014} shows that in the catalogs that exhibit significant levels of assembly bias, using a simple mass-only occupation model can lead to considerable biases in inference of the galaxy--halo connection parameters. Although we cannot rule out moderate level of assembly bias in our findings, we do not find any considerable discrepancy between the two models in terms of estimating the underlying HOD parameters.

A few galaxy--halo connection methods have been proposed in the literature that give rise to assembly bias in the galaxy population. \citet{arz2014} demonstrates that the abundance matching techniques based on $V_{\rm max }$ (as introduced in \citealt{hw2013,reddick2013}) exhibit some levels of assembly bias.

We aim to provide a comparison between the levels of assembly bias in these mock catalogs and the mock catalogs predicted from our constraints on the decorated HOD model for $L_{\star}$ type galaxies. In particular, we consider the abundance matching catalogs produced by \citet{hw2013}. These catalogs have been extensively studied for potential systematic effects of galaxy assembly bias on cosmological (\citealt{edHOD-weinberg}) and HOD (\citealt{arz2014}) inferences. This abundance matching catalog was built based on the $\mathtt{Bolshoi}$ $N$-body simulation (\citealt{Klypin2011}) using the adaptive refinement tree code (ART \citealt{art}). The Box size for this simulation is 250 $h^{-1} \rm{Mpc}$, the number of simulation particles is 2048$^3$, the mass per simulation particle $m_{\rm p}$ is $1.35 \times 10^{8} \; h^{-1} M_{\odot}$, and the gravitational softening length $\epsilon$ is 1 $h^{-1} \rm{kpc}$. The halos and subhalos in this simulation are identified using the ROCKSTAR algorithm (\citealt{rockstar}). 
The \citet{hw2013} catalogs make use of $V_{\rm peak}$ (maximum $V_{\rm max}$ throughout the assembly history of halo) as the subhalo property to be matched to galaxy luminosity.

As noted by both \citet{arz2014},and \citet{edHOD-weinberg}, these galaxy mock catalogs show significant levels of assembly bias. This has been shown by investigating the difference in $w_{p}$ between the randomized mock catalogs and the original mock catalogs. Randomization is performed in a procedure described in \citet{arz2014}. First all central galaxies are shuffled among all halos within each of the halo mass bins (with width of 0.1 dex). In each mass bin, once the centrals have been shuffled, the satellite systems are shuffled among all halos in that mass bin, preserving their relative distance to the center of halo. This procedure preserves the HOD, but erases any dependence of the galaxy population on the assembly history of halos such that, assembly bias is erased in the randomized catalog.

For $L_{\star}$ galaxies, the difference in $w_{p}$ between the randomized and the \citealt{hw2013} catalogs is shown in Figure \ref{fig:randomized} with the red curves. As previously noted by \citet{arz2014} and as it can be seen in Figure $\ref{fig:randomized}$, the difference in $w_{p}$ between these catalogs and their corresponding randomized versions is only significant in large scales. This implies that in these catalogs, only the central galaxies are affected by assembly bias. This is in agreement with our findings.

Furthermore, by making random draws from the posterior pdf over the parameters of the model, creating mock catalogs with these random draws, and computing the difference in $w_{p}$ between the randomized catalogs and the original catalogs (shown with blue curves in Figure \ref{fig:randomized}), we note that our findings follow the same trend. That is, we see no difference in the small scale clustering and significant differences as we move towards larger scales. Similar to \citealt{hw2013} catalogs, assembly bias becomes less significant as we probe brighter galaxy samples. Furthermore, we notice that our mock catalogs favor more modest levels of assembly bias as the fractional difference in $w_{p}$ is smaller in our mock catalogs.
